\chapter{Development Roadmap}
\section{Roadmap and Fundraising Plan}

\subsection{Project Roadmap}

The project development follows a phased approach commencing in 2026 Q1. Initial phase activities encompass fundraising initiatives, core team expansion, official website deployment, white paper publication, and community establishment across Twitter and Discord platforms.

\textbf{2026 Q1} initiates alpha testing of protocol architecture and tokenomics mechanisms, validating core functionality and economic model parameters.

\textbf{2026 Q2} delivers testnet release for public participation, enabling community testing and feedback collection across distributed infrastructure.

\textbf{2026 Q3} launches mainnet for public access alongside Initial DEX Offering (IDO), marking full operational deployment and token distribution commencement.

\subsection{Fundraising Plan}

The fundraising strategy implements a three-stage token allocation approach. Initial offering in 2026 Q1 allocates 5\% of CPT tokens targeting \$4M USD capital raise, providing early supporter access at favorable valuations. Comparative market analysis positions the project against established decentralized computing networks, notably Golem's \$200M valuation with sub-8,000 core infrastructure and \$30K monthly utilization.

Subsequent funding rounds in 2026 Q2 and 2026 Q3 each allocate 5\% of CPT supply at prevailing market valuations, enabling capital acquisition aligned with achieved milestones and demonstrated network growth. Progressive pricing reflects platform maturation and computational resource expansion.