%% TEST TRANSLATION - AutoTranslated (placeholder)

\chapter{Core Team, Foundation and Advisor}

\subsection*{The Core Team}

The Core Team assumes responsibility for establishing, maintaining, and advancing the platform's technical infrastructure. Development and maintenance scope encompasses the CHESS computing power distribution software, quality evaluation systems for listed computing resources, blockchain platform architecture, smart contract implementation, and supporting technical infrastructure.

Team expertise spans distributed high-performance computing, public cloud services, heterogeneous computing architectures, decentralized finance investment strategies, artificial intelligence and Big Data applications, financial technology solutions, distributed system software development, and computing resource commercialization.

\subsubsection*{Core Team Members}

\textbf{Dr. Wai-Mo Suen} brings 25 years of expertise in high-performance computing technologies and modern computing business operations. As Founder and CEO of ClusterTech since 2000, he has delivered HPC, cloud computing, AI, and Big Data solutions while receiving multiple awards recognizing achievements in High-Performance Computing Business and Fintech innovation.

\textbf{Dr. Harry Yu} specializes in FPGA technologies as Founder and CEO of CTAccel, which secured Intel Capital funding in 2018. His investment acumen includes two years of decentralized finance experience achieving an 18\% annualized ROI with a 4.6 Sharpe ratio.

\textbf{Mr. Eric Leung} contributes 15 years of HPC system administration experience complemented by a decade leading operations for a public cloud service provider.

\textbf{Mr. GY Han} provides 15 years of specialized experience in HPC system management software development.

\textbf{Mr. Terence Leung} offers nearly three decades of law enforcement expertise specializing in anti-money laundering and fraud investigations, augmented by extensive compliance and risk management experience. He has served as advisor and financial controller for quantitative and DeFi investment funds for five years.

\textbf{Mr. Pong Po Lam Paul (龐寶林)} founded Pegasus Fund Managers Ltd. and co-founded The Institute of Financial Planners of Hong Kong, The Institute of Financial Technologists of Asia, and the HK Institute of Financial Analysts \& Professional Commentators. His public service encompasses roles with the Financial Services Development Council, MPF Advisory Committee, The Hong Kong Institute of Certified Public Accountants, and Securities \& Futures Commission. He holds Certified Financial Planner (CFPCM) and Certified Financial Technologist (CFT) credentials.

\textbf{Mr. XXX} contributes extensive experience in IT business and marketing operations.

\subsection*{The Foundation, Investors, and SPs}

\subsubsection*{The Foundation}

The Foundation manages project development, promotion, and maintenance to ensure long-term sustainability. Responsibilities encompass token allocation and management, community building and engagement, marketing and promotional initiatives, project governance oversight, and technical and economic ecosystem support.

Foundation composition includes Core Team members and advisors possessing expertise in high-performance and cloud computing resource provisioning, AI and Big Data infrastructure, financial investment strategies, financial product development, and compliance with commercial regulations and anti-money laundering requirements.

\subsubsection*{The Investors}

To be confirmed.

\subsubsection*{The Service Providers (SPs)}

At platform launch, five Certified Service Providers (CSPs) have registered, contributing computational resources comprising xx CPU cores (equivalent to ??? X86 cores) delivering ??? FP64 TFLOPS, yy GPUs (equivalent to xxx TOPS for 32-bit tensor operations), zz FPGAs (equivalent to ??? TFLOPS of FP32 operations), and ??? PB of storage capacity.

Resource growth projections target 10× CPU expansion, 20× GPU scaling, 5× FPGA growth, and 10× storage capacity increase within one year following launch.
